From physical principles to ???

### 2016-03-25 2015CompleteDerivation/completeDerivation.tex
Discussion on discontinuities

The generality of this result explains why in physics one always assumes functions to be well behaved. This is not a matter of practical convenience or usefulness, but it's because continuous functions represent actual physically distinguishable objects.

%TODO: do continuous function form a manifold Hausdorf and second countable?

>>>>

The generality of this result explains why in physics one always assumes functions to be well behaved. As the result was derived from our notion of physical distinguishability, this is not a matter of practical convenience or usefulness. Suppose we were able to prepare a force field that was zero everywhere in space except at a single point. This gives us a way to tag a specific point. A finite precision measurement of the force provides us infinite precision of space, which we ruled out.\footnote{This assumes that we are able to position the probe perfectly, which we could do if we able to manipulate forces at that precision.} This is what the math is telling us, that if we said before that outcomes can't distinguish isolated points (i.e. the topology is second countable) then neither can maps. It is physical consistency that limits us to continuous functions.

While functions with few discontinuities are useful and used in physics and engineering, they are employed for idealized cases  (e.g. a signal change is fast enough, a charge distribution is small enough) that are usually treated differently (i.e. propagation in material discontinuities). While this may be obvious and intuitive to the physicist, it may be troubling to the mathematician as the proper use of many mathematical techniques requires the inclusion of discontinuous functions. This is less of a problem than it would seem at first. Once we made sure that the objects and their relationships are physically meaningful, we can extend our mathematical spaces for the purpose of math computations. Our physically meaningful continuous function can be expanded into a sum of discontinuous functions. One just has to be mindful of the extension and be wary that mathematical results that depend on such extension may or may not be physically meaningful.
